Equalizer 2.0 --\\Convergence of a Parallel Rendering Framework

### 2018-02-08 paperIEEE.tex
minor fixes
git-svn-id: https://dev.ifi.uzh.ch/vmml/svn/Equalizer16@116 db7c848b-7755-4df2-b763-8796797afa52

The ply file is converted into a kd-Tree for fast view frustum culling and
rendering, and the resulting data structure is serialized in binary form for
data transmission.

@@

The ply data is little compressible, the default compressor achieves a 10\%
reduction. This is due to a high entropy in the data and the dominant use of
floating point values. Overall, the profile is similar to the generic benchmark,
at a smaller compression rate.

@@

The David statue at 2\,mm resolution is organized in a kD-tree for rendering. Each
node is a separate distributed object, which has two child node objects. A
total of $1023$ objects is distributed and synchronized. \fig{fDavidDist} shows
the distribution times for this data set. Due to limited compressibility of the
data, the results are relatively similar. Compressing the data repeatedly for
each client leads to decreased performance, since the compression overhead
cannot be amortized by the decreased transmission time. Buffering data slightly
improves performance by reducing the CPU and copy overhead. Combining
compression and buffering leads to the best performance, although only by about
10\%.

@@

\begin{figure*}[ht]\center
  \includegraphics[width=\textwidth]{images/compressorDetail}
  \caption{\label{fCompressorDetail}Data compression for ply data (left, David
    statue 2\,mm) and raw volumes shown in \fig{fVolumes} (middle and right)}
\end{figure*}

>>>>

The PLY file is converted into a k-d tree for fast view frustum culling and
rendering, and the resulting data structure is serialized in binary form for
data transmission.

@@

The PLY data is little compressible, the default compressor achieves a 10\%
reduction. This is due to a high entropy in the data and the dominant use of
floating point values. Overall, the profile is similar to the generic benchmark,
at a smaller compression rate.

@@

The David statue at 2\,mm resolution is organized in a k-d tree for rendering. Each
node is a separate distributed object, which has two child node objects. A
total of $1023$ objects is distributed and synchronized. \fig{fDavidDist} shows
the distribution times for this data set. Due to limited compressibility of the
data, the results are relatively similar. Compressing the data repeatedly for
each client leads to decreased performance, since the compression overhead
cannot be amortized by the decreased transmission time. Buffering data slightly
improves performance by reducing the CPU and copy overhead. Combining
compression and buffering leads to the best performance, although only by about
10\%.

@@

\begin{figure*}[ht]\center
  \includegraphics[width=\textwidth]{images/compressorDetail}
  \caption{\label{fCompressorDetail}Data compression for PLY data (left, David
    statue 2\,mm) and raw volumes shown in \fig{fVolumes} (middle and right)}
\end{figure*}
